Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-09 parallel.tex
Removing the dedner texfile from the Makefile, and fixing up a few missing $'s.

Because of the wide variety of simulations, methods, and uses of \bb{enzo}, it
is difficult to define exactly which routines are most costly during a given
simulation.  As such, we have designed a lightweight registering system that
has been implemented for the most commonly used routines (such as the
hydrodynamic and gravity solvers) as well as refinement level timers that
measure the (exclusive) time spent on each level.  Beyond this minimal set of
routines, we have designed a simple way for the user to modify the source
by adding TIMER_START(``Your Routine Name'') and TIMER_END(``Your Routine
Name'').  These timers are automatically registered in a
std::map\footnote{http://www.cplusplus.com/reference/map/map/}.  These timers
are created and managed individually on each processor in an asynchronous
fashion.

>>>>

Because of the wide variety of simulations, methods, and uses of \bb{enzo}, it
is difficult to define exactly which routines are most costly during a given
simulation.  As such, we have designed a lightweight registering system that
has been implemented for the most commonly used routines (such as the
hydrodynamic and gravity solvers) as well as refinement level timers that
measure the (exclusive) time spent on each level.  Beyond this minimal set of
routines, we have designed a simple way for the user to modify the source
by adding $TIMER_START(``Your Routine Name'')$ and $TIMER_END(``Your Routine
Name'')$.  These timers are automatically registered in a
std::map\footnote{http://www.cplusplus.com/reference/map/map/}.  These timers
are created and managed individually on each processor in an asynchronous
fashion.
